Optimizing DTW-Based Audio-to-MIDI Alignment and Matching

### 2015-12-24 paper.tex
Add acknowledgements
... and remove some text to fit them!

After aligning all pairs in this dataset, we synthesized the resulting aligned MIDI files and created stereo recordings with the aligned synthesized MIDI audio in one channel and the original audio recording in the other.
We then listened to each aligned MIDI pair and annotated a score from 1-5 according to the alignment accuracy, as follows:
\begin{enumerate}[topsep=1pt,itemsep=-1pt]
\item MIDI and audio file are incorrectly matched
\item Alignment failed due to major differences
\item Alignment was mostly successful with minor issues
\item Perfect alignment with minor transcription issues
\item Perfect alignment and transcription
\end{enumerate}
For example, if a MIDI transcription was matched and successfully aligned to the correct song but was missing an instrument, a rating of 4 would be given; if the missing instrument caused the alignment to sound ``sloppy'', the rating would be 3 instead.
Ideally, alignments with low confidence scores (normalized DTW distance) will be given higher ratings, and vice versa.
To prevent biasing the results, we did not have access to the reported confidence score while rating a given aligned pair.

@@

Overall, our ``gold standard'' alignment system was able to successfully align most correctly-matched pairs and produced a reliable confidence score.
Considering pairs rated 3-5 as ``correct'' matches, the resulting confidence scores achieve an area under the ROC curve of 0.981 (95\% confidence interval [.973, .989], calculated by 1000-sample bootstrap), indicating a high quality measure.
Unfortunately, there were a few pairs rated 1 or 2 that still had small normalized DTW scores suggesting a successful alignment (visible as outliers in Figure \ref{fig:violin}); without these outliers, we could use a wider range of thresholds to obtain high-confidence alignments.
The most important remaining flaw is the relative insensitivity to missing instruments and embellishments.
In summary, large-scale optimization over synthetic data has delivered a DTW-based system which is simple to implement and achieves accurate and reliable results for both alignment and matching.
A high-level discussion of these results, with more figures and an implementation of our ``gold standard'' system, is available online,\footnote{\href{http://bit.ly/alignment-overview}{\texttt{http://bit.ly/alignment-overview}}} as is the code used in these experiments.\footnote{\href{https://github.com/craffel/alignment-search}{\texttt{https://github.com/craffel/alignment-search}}}

>>>>

After aligning all pairs in this dataset, we synthesized the resulting aligned MIDI files and created stereo recordings with the aligned synthesized MIDI audio in one channel and the original audio recording in the other.
We then listened to each aligned MIDI pair and annotated a score from 1-5 as follows:
\begin{enumerate}[topsep=1pt,itemsep=-1pt]
\item MIDI and audio file are incorrectly matched
\item Alignment failed due to major differences
\item Alignment was mostly successful with minor issues
\item Perfect alignment with minor transcription issues
\item Perfect alignment and transcription
\end{enumerate}
For example, if a MIDI transcription was matched and successfully aligned to the correct song but was missing an instrument, a rating of 4 would be given; if the missing instrument caused the alignment to sound ``sloppy'', the rating would be 3 instead.
Ideally, alignments with low confidence scores (normalized DTW distance) will be given higher ratings, and vice versa.
To prevent biasing the results, we did not have access to the reported confidence score while rating a given aligned pair.

@@

Overall, our ``gold standard'' alignment system was able to successfully align most correctly-matched pairs and produced a reliable confidence score.
Considering pairs rated 3-5 as ``correct'' matches, the resulting confidence scores achieve an area under the ROC curve of 0.981 (95\% confidence interval [.973, .989], calculated by 1000-sample bootstrap), indicating a high quality measure.
Unfortunately, there were a few pairs rated 1 or 2 that still had small normalized DTW scores suggesting a successful alignment; without these outliers, we could use a wider range of thresholds to obtain high-confidence alignments.
The most important remaining flaw is the relative insensitivity to missing instruments and embellishments.

In summary, large-scale optimization over synthetic data has delivered a DTW-based system which is simple to implement and achieves accurate and reliable results for both alignment and matching.
A high-level discussion of this paper, with more figures and an implementation of our ``gold standard'' system, is available online,\footnote{\href{http://bit.ly/alignment-overview}{\texttt{http://bit.ly/alignment-overview}}} as is the code used in these experiments.\footnote{\href{https://github.com/craffel/alignment-search}{\texttt{https://github.com/craffel/alignment-search}}} 
We thank Hilary Mogul for preliminary work and Dawen Liang for helpful discussion.
